% Declaration of Originality
\frontmatterchapter{Declaration of Originality}

% EDIT FROM HERE
% Example text



I hereby declare that the work presented in this thesis is my own unless otherwise stated. To the best of my knowledge the work is original and ideas developed in collaboration with others have been appropriately referenced.


% Copyright Declaration
\frontmatterchapter{Copyright Declaration}

% EDIT FROM HERE
% Example text


% Note: The copyright declaration must be verbatim one of the 6 options supplied by Imperial College
% See: https://www.imperial.ac.uk/research-and-innovation/support-for-staff/scholarly-communication/open-access/theses/selecting-a-creative-commons-licence/

\textbf{Attribution-NoDerivatives Licence (CC BY-ND 4.0)}

The copyright of this thesis rests with the author. Unless otherwise indicated, its contents are licensed under a \href{https://creativecommons.org/licenses/by-nd/4.0/}{Creative Commons Attribution NoDerivatives 4.0 International Licence}  (CC BY-ND).

Under this licence, you may copy and redistribute the material in any medium or format for both commercial and non-commercial purposes.  This on the condition that; you credit the author and do not distribute modified versions of the work.

When reusing or sharing this work, ensure you make the licence terms clear to others by naming the licence and linking to the licence text.

Please seek permission from the copyright holder for uses of this work that are not included in this licence or permitted under UK Copyright Law.
